---
title: "p8105_hw5_kl3181"
author: Kelley Lou
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
	fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Read in the data and clean.
```{r}
homicide_df = 
  read.csv("./homicide_data/homicide-data.csv") %>% 
  mutate(
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    ),
    city_state = str_c(city, state, sep = "_")
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Create aggregate DF
```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Proportion test for a single city 
```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Iteration for all cities
```{r}
results_df = 
  aggregate_df %>% 
  mutate(
     prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
     tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
   ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

Reading one dataset
```{r}
data_1 = read_csv("lda_data/con_01.csv")
```

```{r}
path_df = 
  tibble(
    path = list.files("lda_data")
  ) %>% 
  mutate(
    path = str_c("lda_data/", path),
    data = map())

read.csv(path_df$path[[1]])
```

mutate/string operation to see if someone is in control or experimental group. 

Observations over time - week 1-8 and observations next to it. (pivot)

Everything should be in one tibble. 


## Problem 3

Simulations!!
Sample from a normal distribution - sample size 30, std 5, change the mean (1 to 6) with 5000 datasets for each different mean. 

Exporting results of hypothesis test to see if mean = 0. (t-test)

See what happens as you move from 0 to 1 and conduct t-test along the way. Start with sim.mean and std function to export t-tests instead

estimate, p-value

plots:
- filter(show results when p value is less than 0.5 and what does the mean look like)
-  
